Readme for Muir and Angert

### 2017-10-13 README.Rmd
test

# card-cline
Grow with the flow: a latitudinal cline in physiology is associated with more variable precipitation in *Erythranthe cardinalis*

@@

## Downloading data and code

1. Download or clone this repository to your machine.
2. Open `card-cline.Rproj` in [RStudio](https://www.rstudio.com/)

>>>>

# card-cline
Grow with the flow: a latitudinal cline in physiology is associated with more variable precipitation in *Erythranthe cardinalis*. In Press at *Journal of Evolutionary Biology*.

@@

## Downloading repository

1. Download or clone this repository to your machine.
2. Open `card-cline.Rproj` in [RStudio](https://www.rstudio.com/)
3. Install R packages if necessary.
